---
title: "EWGrantCryptoFigure"
author: "Liz Hughes and Laura Tuck"
date: "13/03/2022"
output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Cryptococcus Part B2 Figure

This code will produce a  figure that demonstrates that we can successfully transform and do complementation in Cryptococcus, to argue that we should be able to do similar experiments with Ssd1. The Gat201 complementation is the best evidence that we have for that.
A short 3-panel figure showing:
A. Overview of CryptoMobius for gene complementation
B. Simple evidence that we complemented a Gat201 phenotype - I think if there are some clear growth curve or colony assays from @Liz Hughes? The one on the Jan seminar is nice but a bit complicated, too many replicate lines to be clear for a grant application.
C. (maybe) One clear panel showing that we can express a fluorescent protein using CryptoMobius? Microscopy or flow or colonies on plates are fine.

# Load packages

```{r load_packages}
library(reshape2)
library(rlang)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(markdown)
library(cowplot)
library(viridis)
library(flowCore)
library(hrbrthemes)
library(ggridges)
library(extrafont)
library(svglite)

```


```{r install flowcore, eval = FALSE}
#if (!require("BiocManager", quietly = TRUE))
#    install.packages("BiocManager")

#BiocManager::install("flowCore")
# I should only need to run this once when reopening the script, don't run each time!
```
# Panel B

## Plate reader assay.

Set up to test growth of WT and Gat201 complemented strains in RPMI at 37 degrees.
1 Biorep, 4 Techreps each: 3 WT Strains (H99, KN99-alpha and KN99a), Madhani Gat201 deletion mutant and Gat201-complemented strains 23,26,30,32,36,44,46,50,51 and 53.
Grow 5ml culture from colony (1 colony = 1 Biorep)in YPD, 30C, 200 rpm ON.
Seed at OD 600nm = 0.2; 200 ul per well.
Run for 500 cycles.

Note: 
There was condensation on the lid of wells C8 (Gat201-M1.3), C9 (Gat201-M1.4) and C10 (23 1.3) . D8 (36 1.1) and 9 (36 1.2). E9 (36 1.4).
These wells will be removed from the analysis.
The plate was set up and running and by mistake the door was opened and plate removed after about an hour. I put the plate back in and started the run again.


## Read in transposed data as csv file

```{r csv_file}
rawdata1 <- read.csv("../Input/20210608_PR17_TRSP.csv")

```

## Change time in seconds to time in hours

```{r mutate_time}
rawdata_day<-mutate(rawdata1, Time = Time/86400)

```

## Tidy the data using the melt function from reshape2

```{r reshape}
reshaped <- melt(rawdata_day, id=c("Time", "Temp"), variable.name="Well",
                 value.name="OD595")
summary(reshaped)
```

## Read in the Plate map data from csv file

```{r Load_platemap}
platemap <- read.csv("../Input/20210608_PR17_Setup.csv ")

```

## Combine the reshaped data with the plate map, pairing them by Well


```{r combine_files}
annotated <- inner_join(reshaped, platemap, by="Well")
 
```


`


## Calculate median OD for blank wells to use to normalise data.
Remove wells A1, A12, B1, C1, C8, C9, C10, D1, D8, D9, E1, E9, F1, F10, F11, G1 and H1 from the analysis.

```{r calc_blank_medians}

blank_OD_summary <- annotated %>%
       dplyr::filter(Strain=="") %>%
       dplyr::filter(Well!= "A1")%>%
       dplyr::filter(Well!= "A12")%>%
       dplyr::filter(Well!= "B1")%>%
       dplyr::filter(Well!= "C1")%>%
       dplyr::filter(Well!= "D1")%>%
       dplyr::filter(Well!= "E1")%>%
       dplyr::filter(Well!= "F1")%>%
       dplyr::filter(Well!= "F10")%>%
       dplyr::filter(Well!= "F11")%>%
       dplyr::filter(Well!= "G1")%>%
       dplyr::filter(Well!= "H1")%>%
  group_by(Medium) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))

print(blank_OD_summary)
```


## Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs)

```{r NormOD}
normalisedOD <- annotated %>%
            left_join(blank_OD_summary, by="Medium") %>%
            mutate(OD_corrected = OD595 - OD_median) %>%
                dplyr::filter(Well!= "C8")%>%
                dplyr::filter(Well!= "C9")%>%
                dplyr::filter(Well!= "C10")%>%
                dplyr::filter(Well!= "D89")%>%
                dplyr::filter(Well!= "D9")%>%
                dplyr::filter(Well!= "E9")

```


## Re-order the legend to match the order of the lines on the plot

```{r reorder_legend}

normalisedOD$Strain <- factor(normalisedOD$Strain, levels = c("Gat201 deletion", "Clone 2", "Clone 1", "WT1", "WT2"))

```

## Plot


```{r plot_all_stat_summary}

PRPlot <- ggplot(data=normalisedOD %>%
                dplyr::filter(Strain != ""),
                aes(x=Time, y=OD_corrected, colour = Strain)) + 
                stat_summary(fun = "median", geom = "line", size = 1) +
                scale_y_continuous(limits=c(0,0.45),expand=c(0,0)) +
        labs(x = "Number of Days",
             y = "Absorbance (595nm)",
             title = "Gat201 Complemented Clones 1 + 2") +
        theme_classic()
    
PRPlot


```

# Panel C

## Flow_cytometry_analysis_LT_160222

### Define functions to load flow cytometry data, using FlowCore package

```{r functions_load}
repair_flow_colnames <- function(string) {
  string %>%
    stringr::str_replace_all(" ", "") %>%
    stringr::str_replace_all("PE-", "PE") %>%
    stringr::str_replace_all("-", "_")
}

read_fcs_tibble <- function(file,...) {
  read.FCS(file,...) %>%
    .@exprs %>%
    as_tibble %>%
    set_names(repair_flow_colnames(names(.)))
}

```



```{r test_readFCS, eval = FALSE, include = FALSE}
# This is just a test read of one of the .fcs files, need to run the datadir chunk first though!
flowf <- read.FCS("../Input/Flow_cytometry_data/Specimen_001_wt_a.fcs", sep = "/")

flowf

flowf@parameters@data
```

## Load samplesheet

```{r load_samplesheet}
datadir <- "../Input/Flow_cytometry_data/"
#Will need to make a new sample sheet for each new set of strains/bioreps I do
straindir <- "../Input/Flow_cytometry_data/"
# Strain_Order <-  c("KN99ON", "CnLT0004.1ON", "CnLT0004.2ON", "CnLT0004.3ON", "CnLT0007.1ON", "CnLT0007.2ON", "CnLT0007.3ON")

samplesheet <- paste(straindir, "StrainsForFlowCytometry_170222.xlsx", sep = "/") %>%
  readxl::read_excel() %>%
  select(Strain, SampleLabel, Replicate, Filename) %>%
  mutate(SampleLabel = factor(SampleLabel))

samplesheet
```

## Load Data

```{r load_all_data}
#Check the specific gates for the datasets, this is a rough estimate of where the gates lie
flow_data_all <- samplesheet %>%
  group_by(Strain, SampleLabel, Replicate, Filename) %>%
  do( read_fcs_tibble(paste(datadir, .$Filename[1], sep = "/")) )

flow_data_gated_singlets <- flow_data_all %>%
  dplyr::filter(FSC_W > 50000, FSC_W < 90000, 
                FSC_A > 80000, FSC_A < 220000)

flow_data_gated_budding <- flow_data_all %>%
  dplyr::filter(FSC_W > 90000, FSC_W < 150000, 
                FSC_A > 60000, FSC_A < 250000)
```

## Inspect Flow Data

```{r inspect_flow_data}
flow_data_all

left_join(flow_data_all %>%
            group_by(Strain) %>%
            tally(),
          flow_data_gated_singlets %>%
            group_by(Strain) %>%
            tally(),
          by = "Strain",
          suffix = c("_all", "_gated_singlets") )


```

## Plot

```{r plot to show mcardinal fluorescence v cell density using BiorepA cells}

options(scipen = 5)

Strains_ON <- c("KN99ON", "CnLT0004.1ON", "CnLT0004.2ON", "CnLT0004.3ON", "CnLT0007.1ON", "CnLT0007.2ON", "CnLT0007.3ON")
Strains_A <- c("WT", "BR1", "BR2", "BR3")
Strains_B <- c("KN99b", "CnLT0004.1b", "CnLT0004.2b", "CnLT0004.3b", "CnLT0007.1b", "CnLT0007.2b", "CnLT0007.3b")
Strains_C <- c("KN99c", "CnLT0004.1c", "CnLT0004.2c", "CnLT0004.3c", "CnLT0007.1c", "CnLT0007.2c", "CnLT0007.3c")
# flow_data_gated_singlets <- mutate(flow_data_gated_singlets, SampleLabel = factor(SampleLabel, Strain_Order))


mCardinal_Plot <- ggplot(data = dplyr::filter(flow_data_gated_singlets, Strain %in% Strains_A), aes(x = PECy5_A)) +
  geom_density(aes(colour = Strain, lty = Strain, fill = Strain), lwd = 0.8, alpha = 0.1) +
  scale_fill_manual(values = c("darkred", "darkred", "darkred","cyan4")) + 
  scale_color_manual(values = c("darkred", "darkred", "darkred","cyan4")) +
  scale_linetype_manual(values = c("solid", "dashed", "dotted", "solid")) +
  scale_x_log10(limits = c(100, 200000)) +
  labs(title = 'mCardinal Fluorescence vs Cell Density', x = "PECy5_A", y = "Cell density") +
  theme_classic()

 mCardinal_Plot

```


# Draft Multipanel Figure

```{r figure_CryptoMob, fig.width = 7, fig.height = 10}

figure_B2  <-     
    plot_grid(
    PRPlot +
      theme(plot.margin = unit(c(0.1,0,0.5,0.1),"in")),
    mCardinal_Plot,
    theme(plot.margin = unit(c(1,0,0,1),"in")),
       ncol = 1,
    rel_heights = c(1,1),
    labels = c("B","C")
  )


plot_grid(
  figure_B2 ,
  ncol = 1,
  rel_widths = c(2))



```


# Save Multipanel Figure .jpeg, .svg and .Pdf

```{r save_jpeg}
ggsave("../Output/figure_B2 .jpeg", 
figure_B2  ,width = 7,height=10)
```

```{r save_svg}
ggsave("../Output/figure_B2 .svg", 
figure_B2  ,width = 7,height=10)
```

```{r save_pdf}
ggsave("../Output/figure_B2 .pdf", 
figure_B2  ,width = 7,height=10)
```















